Multisensor Architecture for an Intersection Management System

### 2015-10-16 ch3-arch_sys.tex
Updated ch3, added some paragraphs about traffic simulation.

Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors and computing capabilities. Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control step. Also it is needed to test and validate the developments prior to a real and full functional implementation. The first part of this chapter describes the main stages in a intersection management system based on image and range sensors, and the methods used in these stages. Then an architecture proposal for the implementation of such a system is presented. Finally, two validation tools for IMS applications are described, simulation models and datasets.

@@

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering and background subtraction techniques to get the foreground of the scene, remove noise and irrelevant data. Spatio-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, and also is shown how the data volume is reduced while data meaning increases in the last stages.

@@

Depending on system design, if it has multiple sensors of the same type or different type, a data fusion approach should be chosen. When data came from same-type sensors, it is usually fused at low levels using techniques for temporal and/or spatial alignment, depending on sensors configuration. This is the case for a network of lasers or lidars or for multi-camera systems. If the system have different type of sensors, data from them may be fused at mid level, based on extracted features or classes on each subsystem; or may be fused at high level if each subsystem delivers control or decision outputs.

@@

Different tasks could be performed in each aforementioned stages, as is referred in figure \ref{proc_stages_tasks}. Below there is a description of common concepts and methods associated with each of these tasks, some of them are sensor-independent and others are focused on a specific sensor or type of data. Additionally, these tasks could be used as fusion blocks for homogeneous or heterogeneous data.

@@

\subsection{Preprocessing}
\subsubsection{Background subtraction}
\subsubsection{Time-space alignment}
\subsection{Feature Analysis}
\subsubsection{Segmentation}
\subsubsection{Feature extraction}
\subsection{Pattern Recognition}
\subsubsection{Object association}
\subsubsection{Object tracking}
\subsubsection{Object classification}
\subsection{Situation Assessment}

@@

>>>>

Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors manufacturing and computing capabilities. Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control step. Also it is needed to test and validate the developments prior to a real and full functional implementation. The first part of this chapter describes the main stages in a intersection management system based on image and range sensors, and the methods used in these stages. Then an architecture proposal for the implementation of such a system is presented. Finally, two validation tools for IMS applications are described, simulation models and datasets.

@@

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene. Spatial-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, and also is shown how the data volume is reduced while data meaning increases in the last stages.

@@

Depending on system design, if it has multiple sensors of the same type or different type, a data fusion approach should be chosen. When data came from same-type sensors, it is usually fused at low levels using techniques for temporal-spatial alignment, depending on sensors configuration. This is the case for a network of lasers or lidars or for multi-camera systems. If the system have different type of sensors, data from them may be fused at mid level, based on extracted features or classes on each subsystem; or may be fused at high level if each subsystem delivers control or decision outputs.

@@

Different tasks could be performed in each one of aforementioned stages, as is referred in figure \ref{proc_stages_tasks}. Below there is a description of common concepts and methods associated with each of these tasks, some of them are sensor-independent and others are focused on a specific sensor or type of data. Additionally, these tasks could be used as fusion blocks for homogeneous or heterogeneous data.

@@

\subsection{Preprocessing}
\subsubsection{Time-space alignment}
\subsubsection{Background subtraction}
\subsubsection{Filtering}
\subsection{Feature analysis}
\subsubsection{Segmentation}
\subsubsection{Feature extraction}
\subsubsection{Feature selection}
\subsection{Pattern recognition}
\subsubsection{Object association}
\subsubsection{Object tracking}
\subsubsection{Object classification}
\subsection{Situation assessment}

@@

Transportation is a highly complex activity where different elements, like infrastructure, vehicles and pedestrians, affect efficiency, safety and quality of traffic. Intersections are special cases because there exists a high interaction between those mentioned elements making of these places critical points for mobility. For this reason, it is needed to have traffic models to allow the simulation of new policies or deployments intended to enhance transportation.

Three widely-known models for this kind of analysis are macroscopic model, microscopic model and mesoscopic model. The macroscopic model of traffic flow is based on a hydrodynamic analogy, modeling traffic as a fluid process characterized by three main variables, density, volume and speed, and the objective is to describe time-space evolution of those variables.
